INForex: Interactive News Digest for Forex Investors

### 2020-06-23 paper.tex
Submit to cikm 2020 demo -- cjwang.

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Forexast: A Interactive News Digestion for Forex Investors}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Foreign exchange (forex) markets reflect real-world events, local or global.  Thus,  financial news is oftentimes referred to when making predicting the trends of forex. We propose News Forexast,  an interactive web-based system that displays a forex plot alongside with related financial news. Users can locate specific periods when the trading trends in forex markets dramatically change with the visualization of Standard Deviation (SD) events and Directional Change (DC) events. Finally, Forex comes with a keyword filtering function that allows users to filter news with keywords. We aim to make the decision-making process smoother for not only professional financial analysts but also all investors with this accessible and intuitive website.
\end{abstract}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{forex, financial news, standard deviation, directional change}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{teaser.png}
  \caption{Forexast available at http://}
  \Description{}
  \label{fig:teaser}
\end{teaserfigure}

@@

\section{Introduction}
Foreign exchange (Forex) market has been one of the most popular market for decades, with an estimated \$1\  trillion traded every day\cite{YAO200079}. Spot trading, options future and exchange-traded funds(ETFs) are three of many ways of investing strategies adopted in forex markets\cite{TradeForex}. The strategies might vary but they are driven by an intuitive rule of thumb, which is to buy low and sell high\cite{KOOLEN2014144}\cite{Zervos11}. Therefore, whether investors can accurately forecast the prices or trends is extremely crucial. Forex markets are influenced by numerous factors, such as producer price index(PPI), interest rates and politics, in order to consider as many factors as possible to have more comprehensive approaches for forex investment, investors rely on news for them to stay informed. Besides the fact that news usually reflect the real world events, the similar nature of news and forex also makes these two co-dependent. For example, if the Federal Reserve System (Fed) cuts the interest rate, it is more likely that the value of USD would drop, the devaluation would then feed into forex market increasing the demand, thus making another piece of news.

\section{Related Work and Systems}
The dynamics between news and forex markets have been explored from several different aspects. Evans and Lyons proved that news can have significant effects on currency for days\cite{EVANS2005197}, and more specifically macro news can affect currency prices directly and indirectly via order flow\cite{EVANS200826}. There is also more evidence showcasing news and forex trend are correlated, Bauwens, Omrane and Giot show that volatility increases right before the announcement of scheduled news and unscheduled-but-periodic news\cite{BAUWENS20051108}, while Chatrath et al. suggests that prices respond quickly within 5-min of the news release\cite{CHATRATH201442}. With how forex markets and news interact in mind, it is only reasonable to suggest traders should begin their days by reading news commentary to determine the market sentiment and the daily direction for trading\cite{samuels2015trader}.

There are many trading websites which provide useful information for forex investors, and each of them has its own features\cite{ForexWebsites}. For instance, BabyPips\cite{BabyPips} is a friendly website for junior traders, which provides not only forex plots and data but also courses, tutorials and forums for beginners. Bloomberg\cite{Bloomberg} is a well-known news agency. Therefore, besides stocks and currencies data, it also has various categories of news. TradingView\cite{TradingView} provides numerous functions in a page, such as watchlist, alerts, headlines and real-time chats, where users can customize the settings. However, some of their news and forex plot are not put in the same interface, or the times of news and forex are not highlighted. This could neglect the relation between news and forex data. Therefore, our work aims to highlight the connection between the timing of news and forex trends. New Forexast is designed to display the news’ release time as vertical lines on the forex plot to emphasize the order of breaking news and exchange rates. In addition, when users hover on the line, the background colour of the corresponding news would change. 
We also choose to display standard deviation events (SD events) and directional change events (DC events)\cite{7850020} to help users locate the changes within exchange rates, and pay more attention to the changes of trend or where the prices have larger volatility. The features of News Forexast would be introduced more detailed in section 4.

\section{System Structure}

\subsection{Data Collection}
The forex data is from philipperemy/FX-1-Minute-Data\cite{FX-1-Minute-Data}, a repository of github. We choose the EUR/USD index, and use the DateTime Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote and CLOSE Bid Quote columns as our forex data. The time span is from 2019/08/04 to 2019/09/13 except Saturdays, and the granularity of data is minute.

The news data is crawled by us, containing titles, sources, release times and urls. There are 1116 news in total and the sources are all from The Wall Street Journal\cite{WSJ}.

\subsection{Algorithms for DC and SC events}
To mark some special time points on the plot, we use two algorithms, standard deviation events (SD events) and directional change events (DC events)\cite{7850020}. SD events show the times where the prices dramatically change, and DC events show the times where the trends change. To get these events, we need to calculate the difference rate list $D$ of the price list first. 
Let $P= [p_1, p_2, ..., p_n]$, where $p_t$ stands for the CLOSE Bid Quote at minute $t$ and n equals to total numbers of daily forex data. Then we can get a difference rate list $D= [d_1, d_2, ..., d_m]$, where $d_t = \frac{p_{t+w}-p_t}{p_t}$.  $w\in\mathbb Z^+$ means the range in minutes, which can be freely customized (we use 30 in this demonstration).
$\sigma$ is the standard deviation of $D$, which can be interpreted as the volatility of prices. We use $\sigma$ as our low threshold to attain a subset of D, whose elements are all bigger than $\sigma$. Then the corresponding set of p will be marked as SD events. We also consider $2\sigma$ and $3\sigma$ as medium and high thresholds in our demonstration. Higher threshold will find less events.

Under the DC framework, the market is summarized into alternating uptrends and downtrends\cite{7850020}. A DC event, including a start point and an end point, can be seen as a period that the trend starts to change. At first, we do not know the prices start with a upward or downward trend, so we let the first element of price $p_1$ as a base. Then we start looking through the list until we find a current price $p_c$, where $|\frac{p_c-p_1}{p_1}| > \theta$, $\theta$ can be set to $\sigma$, $2\sigma$, $3\sigma$ as above mentioned. If $p_c > p_1$, that means the span from $p_1$ to $p_c$ is an upward DC event; otherwise, it is a downward DC event. After finding the first DC event, we still have to look through the rest. Let us consider a market starts with a downtrend, which means we are now in an downtrend and waiting for a next uptrend. We keep updating the lowest price $p_l$ in this downtrend until we find a current price $p_c$ that $\frac{p_c-p_l}{p_l} > \theta$. Then, we mark that the span from $p_l$ to $p_c$ is a upward DC event, and the trend become upward. Similarly, if a market is in a uptrend, we keep updating the highest price $p_h$ until we find a current $p_c$ that $\frac{p_h-p_c}{p_c} > \theta$, then $p_h$ to $p_c$ is a downward DC event, and the trend become downward. After finishing looking through all daily forex data, we can get a series of alternating DC events.

\section{Interfaces and features}
The interface of News Forexast can be divided into two main parts, a forex chart and the news section. Users can customize the selection criteria either by directly manipulating the forex chart or applying the keyword filters.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{hover.png}
  \caption{Example of news being highlighted when the cursor hovers over the corresponding timeline on the chart.}
  \Description{}
\end{figure}

\subsection{Interactive Forex Chart}
The forex chart is a standard candlestick chart, powered by Plotly graphing libraries\cite{Plotly}, that displays price movements, users can specify the date they are interested in with the calendar icon above the chart. Supported by Plotly graphing library, users can explore the chart freely by zooming in or dragging out the time frame they are interested. The corresponding news would be highlighted if users hover over the corresponding blue line on the chart. (Fig. 2)

Below the calendar is where users can specify event types and the corresponding thresholds. After selecting an event type and their thresholds, eg. SD and low threshold,  the algorithmic output would be shown on the forex chart. Once done with a specific setting, users can clear the setting with the “clear all” button the top-right. The news section without any specification would show all daily news with titles, released time and sources. Users could link to the original posts and websites by clicking on the news cards.

\subsection{Forex Event Identifier}
With the help of SD and DC events as indicators, users can now spot specific time ranges they are interested in. (Fig 3, 4) Users can then select such time range on the plot and narrow down the news shown on the right to the time range they selected. For example, users can specify 2019/08/30 with the SD with the low threshold, users can tell that there’s a dramatic change during 14:30-16:30 and can proceed to select the time range on the plot. In return, the news section would display related news such as "Would Warren Buffett Buy Greenland?" and "Risky Seller Financing Flourishes Where Homes Are Cheapest".

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sd.png}
  \caption{Examples of displaying SD events on 2019/08/30. The top is set to low threshold and the bottom is set to high threshold. Due to the higher sensitivity, almost all events of the latter are in the slump period around 16:00.}
  \Description{}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{dc.png}
  \caption{Examples of displaying DC events on 2019/08/30. The top is set to low threshold and the bottom is set to high threshold. Due to the higher sensitivity, the latter only summarize the daily market into a downtrend and an uptrend.}
  \Description{}
\end{figure}

\subsection{Customizable Keyword Filter
}
If interested in more specific news, users can use the button under the plot to filter out news with selected keywords. We have placed several keywords such as U.S. and Trump, users can also customize their own tags by clicking the “+” button. For example, if the time frame is specified and the tag "U.S" is applied, only "Strength in U.S. Consumer Spending Drives Economy". would be shown on the news section.(Fig 5)

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{news.png}
  \caption{Examples of filtering news on 2019/08/30. From left to right are none, keyword: 'U.S.', time: '14:30-16:30', and both.}
  \Description{}
\end{figure}

\section{Conclusion and Future work}
We have proposed an interactive website that juxtaposes a forex chart with news within the time frame users selecting. By having the chart and related news side by side together, users, financial professional or amateur investors, can all understand the trend quicker and easier. We are working toward to provide real-time news update in the future, as fixed data is limited. In addition, if we are able to collect more user's log data and news in the future, along with machine learning and natural language processing (NLP) techniques, we can achieve more customized news feed such as personal news recommendation.

\section{Acknowledgments}

>>>>

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Online '20]{Online '20: 29th ACM International Conference on Information and Knowledge Management }{October 19--023, 2020}{Online}
\acmBooktitle{ }
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
% \title{INForex: An Interactive News Digestion for Forex Investors}
  \title{INForex: Interactive News Digest for Forex Investors}   % AMH: check

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{Yi-Shyuan Chiang}
\authornote{These authors contributed equally to this work; author order was determined alphabetically.}
\email{yschiang@gapp.nthu.edu.tw}
\affiliation{%
  \institution{Research Center for Information Technology Innovation, Academia Sinica}
  \city{Taipei}
  \country{Taiwan}}

\author{Chih-Hen Lee}
\authornotemark[1]
\email{ch.lee@citi.sinica.edu.tw}
\affiliation{%
  \institution{Research Center for Information Technology Innovation, Academia Sinica}
  \city{Taipei}
  \country{Taiwan}}

\author{Chuan-Ju Wang}
\email{cjwang@citi.sinica.edu.tw}
\affiliation{%
  \institution{Research Center for Information Technology Innovation, Academia Sinica}
  \city{Taipei}
  \country{Taiwan}}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Chiang, Lee, and Wang}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
As foreign exchange (Forex) markets reflect real-world events, locally or
globally,
financial news is often leveraged to predict Forex trends.
In this demonstration, we propose INForex, an interactive web-based system that
displays a Forex plot alongside related financial news.
To our best knowledge, this is the first system to successfully align the
presentation of two types of time-series data---Forex data and textual
news data---in a unified and time-aware manner. 
Specifically, we first present two event detection methods based on the
standard deviation (SD) and directional change (DC) of the Forex data and use
these to locate specific periods during which prices or trends in Forex markets
change dramatically.
Moreover, INForex includes a keyword filtering function with which users can
filter news with self-defined keywords.
The system can be of great help in revealing valuable insight and relations
between the two types of data and is thus valuable for decision making
not only for professional financial analysts or traders but also for common
investors.
The system is available online at~\url{http://chlee.pythonanywhere.com/forex/}.
\end{abstract}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Forex, financial news, standard deviation, directional change}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{teaser.pdf}
  \caption{INForex available at~\url{http://chlee.pythonanywhere.com/forex/}}
  \Description{}
  \label{fig:teaser}
\end{teaserfigure}

@@

\section{Introduction}
The foreign exchange (Forex) market has been one of the most popular financial
markets for decades, with an estimated \$1\ trillion traded every
day~\cite{YAO200079}.
Spot trading, currency options, currency futures, and currency exchange-traded
funds (ETFs) are four major ways to trade Forex~\cite{TradeForex}.
The strategies might vary but they are driven by an intuitive rule of thumb,
which is to buy low and sell high~\cite{KOOLEN2014144,Zervos11}.
Therefore, the crucial question is whether investors can accurately forecast 
prices or trends.

Forex markets are influenced by numerous factors, including producer price index
(PPI), interest rates, and politics.
In order to consider as many factors as possible to gain a more comprehensive
view for Forex investment, most investors stay informed by relying on news.
Besides the fact that news usually reflects real-world events, the similar
nature of news and Forex also makes these two co-dependent.
For example, if the Federal Reserve System (the Fed) cuts the interest rate, it is
more likely that the value of USD will drop; also, such a devaluation will
later be the subject of another piece of news~\cite{"CNBC"}.

Considering the critical role of news for Forex investment, in this
demonstration, we propose INForex, an interactive web-based system that
displays a Forex plot alongside related financial news.
With the proposed system we seek to align the timing of Forex and news data 
to highlight the connection between these two types of time-series data.
In INForex the release time of news stories is displayed as vertical lines on the
Forex plot to emphasize the order of breaking news and exchange rates. In
addition, when users hover on a vertical line, the background color of the
corresponding news changes. 
Moreover, we propose using two event detection methods based on the standard
deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to
locate specific periods during which the prices or trends in Forex markets change dramatically.
Via this design, we assist users by putting the focus on changes of trend or periods 
of large price volatility.
INForex also comes with a keyword filtering function that allows users to
filter news with self-defined keywords.
To our best knowledge, this is the first system that effectively visualizes these two
types of time-series data---Forex data and textual news data---in a
unified and time-aware manner. 
The proposed INForex can be of great help in revealing valuable insight and
relations between the two types of data and is thus valuable for
decision-making not only for professional financial analysts or traders but
also for common investors.

The remainder of this paper is organized as follows.
In Section~\ref{sec:related}, we review previous studies related to Forex and
news and major websites for Forex traders.
Section~\ref{sec:system} describes the proposed system with details related to
data collection, event detection algorithms, interface, and key features.
After that, we provide a case study in Section~\ref{sec:case}, and
conclude and suggest future work in Section~\ref{sec:conclude}.

\section{Related Work and Systems}\label{sec:related}
The dynamics between news and Forex markets have been explored from several
different aspects.
Evans and Lyons~(2005) prove that news can have significant effects on currency
for days~\cite{EVANS2005197}, and macro news can affect currency prices
directly and indirectly via order flow~\cite{EVANS200826}.
There is other evidence showing that news and Forex trend are correlated as well.
For instance, Bauwens et al.~(2005) show that volatility increases right
before the announcement of scheduled news and unscheduled-but-periodic
news~\cite{BAUWENS20051108}, whereas Chatrath et al.~(2014) suggest that prices
respond within a mere 5 minutes after the news release~\cite{CHATRATH201442}.
Keeping in mind how Forex markets and news interact, it is reasonable for traders
to begin their days by reading news commentary to determine the market
sentiment and the direction for trading~\cite{samuels2015trader}.

Apart from the literature discussing the relation between Forex and news, 
many trading websites provide useful information for Forex investors,
each of which has its own features and limitations~\cite{ForexWebsites}.
For instance, BabyPips\footnote{\url{https://www.babypips.com}} is a friendly
website for junior traders, providing not only Forex plots but also courses,
tutorials, and forums for beginners.
Bloomberg\footnote{\url{https://www.bloomberg.com}} is a well-known news
agency; thus, in addition to currency data and plots, it also provides various
categories of news for users to focus on.
TradingView\footnote{\url{https://www.tradingview.com}} provides numerous
functions in a page, including watchlist, alerts, headlines, and real-time chats,
where users can customize the settings. 
However, most of these websites do not put news and the Forex plot on the same
page, or do not explicitly align the news release times with the Forex prices.
Most neglect the time-dependent relation between news and Forex data
and thus do not effectively visualize these two types of time-series data in a
unified and time-aware manner.

\section{System Description}\label{sec:system}

\subsection{Data Collection}
The Forex data was collected from
philipperemy/FX-1-Minute-Data.\footnote{\url{https://github.com/philipperemy/FX-1-Minute-Data}}
For demonstration purposes, we chose the EUR/USD index and used the DateTime
Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote, and CLOSE Bid Quote
columns to plot the Forex candlestick chart; moreover, the time span for the
Forex data is from August 4, 2019 to September 13, 2019, and the granularity of
data is minute. 
As for news, we crawled articles from The Wall Street
Journal,\footnote{\url{https://www.wsj.com}} each of which contains the title,
the source, the release time, and the corresponding URL.
In this demonstration, there are 1,116 articles in total.

\subsection{Event Detection Algorithms}\label{sec:algo}
The proposed system comes with two event detection algorithms: one based on
the standard deviation of Forex price differences (referred as SD events
hereafter) and one based on the directional change of Forex prices (referred
as DC events hereafter)~\cite{7850020}. 
Specifically, SD events indicate time points during which the Forex prices
dramatically change, whereas DC events show time points during which the trends of
Forex prices change.

We here briefly describe the two algorithms.
Let $P= [p_1, p_2, ..., p_n]$ denote a series of Forex prices, where $p_t$
stands for the CLOSE Bid Quote at minute~$t$ and $n$ equals the total
numbers of daily Forex data; also, the series of difference rates between two
Forex prices is defined as $\mathcal{D}= [d_1, d_2, ..., d_m]$, where $d_t =
{(p_{t+w}-p_t)}/{p_t}$ and $w\in\mathbb Z^+$ denotes the range in minutes.
Note that we set $w=20$ in our prototype system.
We first calculate the standard deviation of differences in list~$\mathcal{D}$
and denote this as $\sigma_\mathcal{D}$; we then use the $z$-score of each
difference to determine the events (i.e.,
$z_{d_i}=(|d_i-m_{\mathcal{D}}|)/\sigma_{\mathcal{D}}>\tau$), where
$m_{\mathcal{D}}$ denotes the mean of the list~$\mathcal{D}$.)
In this demonstration, we consider $\tau=1,2,3$ as our thresholds 
corresponding to labels \emph{Low}, \emph{Medium}, and \emph{High} in the
system. 
Note that a higher threshold locates fewer events.

As for the DC events, the market is summarized into a set of uptrend and
downtrend events~\cite{7850020}.
A DC event, which includes a start point and an end point, can be seen as a period
during which the trend starts to change.
Initially, we use the first element in the price list~$p_1$ as the starting point
of the algorithm; then, the algorithm starts looking through the price list~$P$
in a sequential manner until it locates a price~$p_c$ for which
$|{(p_c-p_1)}/{p_1}|>\theta$.
In this demonstration, we consider
$\theta=\sigma_{\mathcal{D}},2\sigma_{\mathcal{D}},3\sigma_{\mathcal{D}}$ as
our thresholds, corresponding to labels \emph{Low},
\emph{Medium}, and \emph{High} in the system.
If $p_c > p_1$, the span from $p_1$ to $p_c$ denotes an upward DC event;
otherwise, it is a downward DC event.
After finding the first DC event, we look for other DC events in the
rest of the price sequence.
Let us consider a market starting with a downtrend, meaning that the Forex market
is now in a downtrend and waiting for a next uptrend: we continue
updating the lowest price $p_\ell$ in this downtrend until we find a 
price~$p_k$ for which ${(p_k-p_\ell)}/{p_\ell}>\theta$. Then, we note that the span from
$p_\ell$ to $p_k$ is an upward DC event, and the trend becomes an upward one.
Similarly, if a market is in an uptrend, we continue to update the highest 
price~$p_h$ in this uptrend until we find a price~$p_k$ for which
${(p_h-p_k)}/{p_h}>\theta$, in which case the ``$p_h$-to-$p_c$'' spans a downward DC
event, and the trend becomes a downward one.
After finishing examining all the daily Forex data, we have a series of DC events.

\subsection{Interfaces and features}
The INForex interface can be divided into two main parts: 1) the Forex chart
(in the left panel of the system) and 2) the news section (the right panel).
Users customize the selection criteria either by directly
manipulating the Forex chart or applying keyword filters.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{hover.pdf}
  \caption{The interfaces of INForex. Note that news is highlighted when the cursor hovers over the
  corresponding timeline on the chart. The yellow interval is the news
  selection range which can be decided by users.}
  \label{fig:hover}
\end{figure}

\subsubsection{Interactive Forex Chart}
Forex prices are displayed by a standard candlestick chart, powered by
Plotly graphing
libraries.\footnote{\url{https://https://plotly.com/graphing-libraries/}}
Users specify the date they are interested in with the calendar icon above
the chart and then explore the chart freely by zooming in or dragging out the
time frame of interest.
Except for the Forex chart, the blue vertical lines correspond to the news story
release time points. 
As shown in Figure~\ref{fig:hover}, the corresponding news in the right panel
is highlighted if users hover over the corresponding blue line on the chart.
Users also link to the original posts and websites by clicking on the news
cards.
Moreover, users can easily spot specific time ranges of interest
by single-clicking the start and end points of a period on the Forex chart
(resulting in the yellow span in the figure); the news section in the right
panel changes correspondingly according to the selected time span.

\subsubsection{Forex Event Identifier}
Users specify event types (i.e., SD or DC)  and the corresponding thresholds (i.e., Low, Medium, or High) with the Forex event identifier (see the buttoms below the date selection calendar in Figure~\ref{fig:hover}), after which the algorithm output is shown on the Forex chart as
gray dots for the SD events and span lines for the DC events (e.g., see
Figures~\ref{fig:SD} and~\ref{fig:DC} for examples of SD and DC events,
respectively).
For example, users specify August 30, 2019 and select the ``SD'' event with
the ``Low'' threshold; from the upper panel of Figure~\ref{fig:SD}, users 
observe a dramatic change from 14:30 to 16:30 on this day (see the red box in the figure) and 
proceed to select a specific time range on the plot. 
In return, the news section displays related news such as ``Would Warren
Buffett Buy Greenland?'' and ``Risky Seller Financing Flourishes Where Homes
Are Cheapest''. 
Note that once done with a specific setting, users clear the setting with
the ``clear all'' button on the top-right of the left panel;
a higher threshold (the lower panels in Figures~\ref{fig:SD}
and~\ref{fig:DC}) locates fewer events.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sd.pdf}
  \caption{Display of SD events on August 30, 2019. The upper panel
  is set to the ``Low'' threshold and the lower one is set to the ``High''
  threshold.}
  \Description{}
  \label{fig:SD}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{dc.pdf}
  \caption{Display of DC events on August 30, 2019. Upper panel
  set to ``Low'', lower panel to ``High''.}
  \Description{}
  \label{fig:DC}
\end{figure}

\subsubsection{Customizable Keyword Filter
}
If users are interested in more specific news, they use the tags under the
plot to filter out news with selected keywords.
As examples, we have placed several major keywords such as ``U.S.'' and ``Trump'';
users customize their own tags by clicking the ``+'' button.
Figure~\ref{fig:keywords} shows the displayed news based on different keywords
and time filters.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{news.pdf}
  \caption{Filtering news on August 30, 2019. From left to right
  are none, keyword: ``U.S.'', time: `14:30--16:30', and both.}
  \Description{}
  \label{fig:keywords}
\end{figure}

\section{Case Study}\label{sec:case}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{case.pdf}
  \caption{Case study}
  \Description{}
  \label{fig:case}
\end{figure}

In this section, we provide an example to show the strong relation among
events, news, and Forex, as shown in Figure~\ref{fig:case}.
On August 6, 2019, we see that the ``Welcome to Turnaround Tuesday''
article released at 08:43, the time when an uptrend is about to end; note that the DC
event with the High threshold shows that this uptrend starts at 05:07.
The news mentions ``U.S. stock futures were in a decidedly better mood as
Tuesday began than on Monday'', indicating that U.S. stock is likely to rebound
later, thus causing appreciation on USD.
Then, the EUR/USD starts a downtrend from 08:49 to 14:41.
Note lower rates for EUR/USD could be due to a relatively high value for USD.

\section{Conclusion and Future work}\label{sec:conclude}
In this paper, we propose INForex, an interactive system that aligns the
presentation of Forex data and textual news data in a unified and
time-aware manner.
By placing the chart and related news side by side, users, financial
professionals, and amateur investors all understand Forex trends
quicker and easier.
Beyond the presentation in this paper, we are now working toward providing
real-time news updates in the system.
In addition, with the collected browsing behavior from users, we hope to
provide more customized news feed via a personalized news recommender system
by leveraging machine learning and natural language processing techniques.

\section{Acknowledgments}
We thank Po-Chuan Chien for collecting the news articles and Chen-Hung Pai for providing valuable comments regarding the design of the proposed system.
This project was supported in part by the Ministry of Science and Technology in Taiwan under the grants MOST 108-2218-E-009-049.
